Manuscript Figures for Genome Biology

### 2018-05-15 manuscript_figures/manuscript_figures.Rmd
Add Scott methods to RNA-seq case studies/sims
Since DESeq gives a Wald statistic that has a theoretical normal
distribution, the assumptions of the Scott (FDRreg) are met.
This commit adds the Scott method (theoretical and empirical)
back into the RNA-seq case studies as well as the yeast and
polyester simulations.
Add Scott to RNA-seq heatmaps; save 2E separately

# Figure 2D: Some methods are tailored to detecting smaller effect sizes
p4 <- covariateLinePlot(de5, alpha=0.05, covname="log2FC", trans="log1p",
                        nbins=25)
leg <- get_legend(p4)
p4 <- p4 + theme(legend.position="none")

# Figure 2E - upsetr plot -- this solution currently chops off left margin hist
aggupset(de5, alpha=alpha, supplementary = FALSE, 
                       return_list = FALSE, nintersects = 12)
grid.text("Mean overlap Over 100 Replications", x = 0.6, y = 0.97, 
          gp = gpar(fontsize = 16, fontface = "bold")) 
p5 <- grid.grab()

# Figure 2 (ALL)
Fig2 <- plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))

Fig2 <- plot_grid(Fig2, p5, ncol=1, rel_heights = c(1, 0.5),
               labels = c("", "E"), label_size = 20)

Fig2
ggsave(file.path(outdir, "Figure2.pdf"), width=10, height=12)
```

@@

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Covariate") + 
  ggtitle("GWAS")
```

@@

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("RNA-seq")
```

@@

```{r}
TODO
```

@@

```{r}
TODO
```

>>>>

# Figure 2D: Some methods are tailored to detecting smaller effect sizes
p4 <- covariateLinePlot(de5, alpha=0.05, covname="ind_covariate", trans="log1p",
                        nbins=25)
leg <- get_legend(p4)
p4 <- p4 + theme(legend.position="none") + 
  ggtitle("Mean % significant by covariate %ile") + 
  theme(axis.title = element_text(face="bold", size = 10),
        plot.title = element_text(face="bold", size = 14)) +
  xlab("Independent covariate percentile")

# Figure 2E - upsetr plot - save separately
pdf(file.path(outdir, "Figure2E.pdf"), width = 10, height = 4, onefile=FALSE)
aggupset(de5, alpha=alpha, supplementary = FALSE, 
                       return_list = FALSE, nintersects = 12)
grid.text("Mean overlap Over 100 Replications", x = 0.6, y = 0.97, 
          gp = gpar(fontsize = 16, fontface = "bold"))
grid.text("E", x = 0.02, y = 0.97, 
          gp = gpar(fontsize = 24, fontface = "bold")) 
dev.off()

# Figure 2 (ALL)
Fig2 <- plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))
Fig2
ggsave(file.path(outdir, "Figure2A-D.pdf"), width=10, height=8)

```

@@

Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                        excludeMethods = NULL)
Fig4
ggsave(file.path(outdir, "Figure4_all.pdf"), width=6, height=4)

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Covariate",
                excludeMethods = NULL) + 
  ggtitle("GWAS")
```

@@

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", 
                excludeMethods = NULL) + 
  ggtitle("RNA-seq")
```

@@

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL)
```

@@

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|null"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL)
```
